### 2021-01-15 paper/localpsf.tex
lots of edits based on discussion with Noemi and Tucker today. More edits to come

Let $\delta_x$ denote the point source (delta distribution) centered at $x$. The function $\phi_x$ is called the impulse response because straightforward analysis shows that it may be expressed as follows:
\begin{equation}
\label{eq:impulse_response_delta_action}
	\phi_x = \left\langle \mathcal{A}, \delta_x \right\rangle^*,
\end{equation}
where $\left\langle \mathcal{A}, \delta_x \right\rangle \in L^2(\Omega)'$ denotes the result of applying the operator $\mathcal{A}$ to the distribution $\delta_x$, and $\left\langle \mathcal{A}, \delta_x \right\rangle^* \in L^2(\Omega)$ denotes the Riesz representation of $\langle\mathcal{A}, \delta_x\rangle$ with respect to the $L^2$ inner product.\footnote{Recall that the Riesz representative of a functional $\psi \in L^2(\Omega)'$ with respect to the $L^2$ inner product is the unique function $\psi^* \in L^2(\Omega)$ such that $\psi(v) = \left(\psi^*,v\right)_{L^2(\Omega)}$ for all $v \in L^2(\Omega)$.} The local support property says, therefore, that a point source at $x$ has zero impact (or minimal impact) on points $y$ that are far away from $x$.

Note that while the domain of $\mathcal{A}$ is defined as $L^2(\Omega)$, which does not contain the delta distribution, the action of $\mathcal{A}$ may be extended to distributions in a natural way, as described in Appendix \ref{app:distributions}. The action of $\mathcal{A}$ on a distribution $\mu$ is written as $\langle \mathcal{A}, \mu \rangle$. We use this angle bracket notation to distinguish the action of $\mathcal{A}$ on distributions from the action of $\mathcal{A}$ on functions.
%We take the Riesz representative of the linear functional $\left\langle \mathcal{A}, \delta_x \right\rangle \in L^2(\Omega)'$ to convert it into a function $\left\langle \mathcal{A}, \delta_x \right\rangle^* \in L^2(\Omega)$. 
After discretization, the process of applying $\mathcal{A}$ to a distribution, $\mu$, then forming the Riesz representative of the resulting linear functional, amounts to computing $\mathbf{M}^{-1}\mathbf{A} \mathbf{M}^{-1} \boldsymbol{\mu}$, where $\mathbf{A}$, and $\boldsymbol{\mu}$ are discretized versions of $A$ and $\delta_x$, respectively, and $\mathbf{M}$ is a mass matrix (e.g., in a finite element context).

@@

We compute one ``batch'' of $\varphi_i$'s by applying $\mathcal{A}$ to a Dirac comb, then post-processing the result. First, we compute
\begin{equation}
\label{eq:eta_intro}
\eta := \left\langle \mathcal{A}, \xi \right\rangle^*
\end{equation}
where 
\begin{equation*}
	\xi := \sum_{i=1}^l \delta_{x_i}
\end{equation*}
is the Dirac comb associated with point sources centered at a collection of scattered points $x_i$. The batch of points $x_i$ are chosen so that the support of $\phi_{x_i}$ and the support of $\phi_{x_j}$ do not overlap (or do not overlap much) if $i \neq j$. By linearity, and the expression for $\phi_x$ in \eqref{eq:impulse_response_delta_action}, we have
\begin{equation*}
\eta = \sum_{i=1}^l \phi_{x_i}.
\end{equation*}
We may therefore post-process $\eta$ to recover $\phi_{x_i}$ for all of the points $x_i$ in the batch. Since $\varphi_i$ is a translated versions of $\phi_{x_i}$, we also recover $\varphi_i$ for all points $x_i$ in the batch---by applying $\mathcal{A}$ to one distribution, we compute many $\varphi_i$. This is illustrated in Figure FIG. The process is repeated to get more batches of $\varphi_i$'s, until a desired number of batches is reached.

@@

\section*{Acknowledgments}
We thank J.J. Alger for helpful discussions

>>>>

Let $\delta_x$ denote the point source (delta distribution) centered at $x$. The function $\phi_x$ is called the impulse response because straightforward analysis shows that it may be expressed as follows:
\begin{equation}
\label{eq:impulse_response_delta_action}
	\phi_x = \left\langle \mathcal{A}, \delta_x \right\rangle^*,
\end{equation}
where $\left\langle \mathcal{A}, \delta_x \right\rangle \in L^2(\Omega)'$ denotes the result of applying the operator $\mathcal{A}$ to the distribution $\delta_x$, and $\left\langle \mathcal{A}, \delta_x \right\rangle^* \in L^2(\Omega)$ denotes the Riesz representation of $\langle\mathcal{A}, \delta_x\rangle$ with respect to the $L^2$ inner product.\footnote{Recall that the Riesz representative of a functional $\psi \in L^2(\Omega)'$ with respect to the $L^2$ inner product is the unique function $\psi^* \in L^2(\Omega)$ such that $\psi(v) = \left(\psi^*,v\right)_{L^2(\Omega)}$ for all $v \in L^2(\Omega)$.} The local support property says, therefore, that a point source at $x$ has zero impact (or minimal impact) on points $y$ that are far from $x$.

Note that while the domain of $\mathcal{A}$ is defined as $L^2(\Omega)$, which does not contain the delta distribution, the action of $\mathcal{A}$ may be extended to distributions in a natural way, as described in Appendix \ref{app:distributions}. The action of $\mathcal{A}$ on a distribution $\mu$ is written as $\langle \mathcal{A}, \mu \rangle$. We use this angle bracket notation to distinguish the action of $\mathcal{A}$ on distributions from the action of $\mathcal{A}$ on functions.
%We take the Riesz representative of the linear functional $\left\langle \mathcal{A}, \delta_x \right\rangle \in L^2(\Omega)'$ to convert it into a function $\left\langle \mathcal{A}, \delta_x \right\rangle^* \in L^2(\Omega)$. 
After discretization, the process of applying $\mathcal{A}$ to the distribution $\delta_x$, then forming the Riesz representative of the resulting linear functional, amounts to computing $\boldsymbol{\phi}_x = \mathbf{M}^{-1}\mathbf{A} \mathbf{M}^{-1} \boldsymbol{\delta}_x$, where $\boldsymbol{\phi}_x$, $\mathbf{A}$, and $\boldsymbol{\delta}_x$ are discretized versions of $\phi_x$, $A$ and $\delta_x$, respectively, and $\mathbf{M}$ is a mass matrix (e.g., in a finite element context).

@@

We compute one ``batch'' of $\varphi_i$'s by applying $\mathcal{A}$ to a Dirac comb, then post-processing the result. First, we compute
\begin{equation}
\label{eq:eta_intro}
\eta := \left\langle \mathcal{A}, \xi \right\rangle^*
\end{equation}
where 
\begin{equation*}
	\xi := \sum_{i=1}^l \delta_{x_i}
\end{equation*}
is the Dirac comb associated with point sources centered at a collection of scattered points $x_i$. The batch of points $x_i$ are chosen so that the support of $\phi_{x_i}$ and the support of $\phi_{x_j}$ do not overlap (or do not overlap much) if $i \neq j$. By linearity, and the expression for $\phi_x$ in \eqref{eq:impulse_response_delta_action}, we have
\begin{equation*}
\eta = \sum_{i=1}^l \phi_{x_i}.
\end{equation*}
We may therefore post-process $\eta$ to recover $\phi_{x_i}$ for all of the points $x_i$ in the batch. Since $\varphi_i$ is a translated versions of $\phi_{x_i}$, we also recover $\varphi_i$ for all points $x_i$ in the batch. This is illustrated in Figure FIG. The process is repeated to get more batches of $\varphi_i$'s, until a desired number of batches is reached.

@@

\section*{Acknowledgments}
We thank J.J. Alger and Longfei Gao for helpful discussions.
